Exploratory data analysis

### 2019-06-24 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE)

# load drake objects
loadd(vi_data, nri_data, bands_data, coords_vi_nri_clean,

@@

```{r eda-1 }
intro <- introduce(vi_data)
intro_df <- data.frame(
  "Name" = c("Rows", "Columns",
             "Discrete columns", "Continuous columns", "All missing columns",
             "Missing observations", "Complete Rows",
             "Total observations"),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
knitr::kable(intro_df)
```

@@

```{r eda-5 }
intro <- introduce(nri_data)
intro_df <- data.frame(
  "Name" = c("Rows", "Columns",
             "Discrete columns", "Continuous columns", "All missing columns",
             "Missing observations", "Complete Rows",
             "Total observations"),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-8 }
intro <- introduce(bands_data)
intro_df <- data.frame(
  "Name" = c("Rows", "Columns",
             "Discrete columns", "Continuous columns", "All missing columns",
             "Missing observations", "Complete Rows",
             "Total observations"),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(479, 451, 300, 529)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points, 
                                         allpairs = TRUE, 
                                         lonlat = FALSE)))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```

@@

fv_all = dplyr::bind_rows(fv_vi_car$data, 
                          fv_vi_info.gain$data, 
                          fv_vi_gain.ratio$data,
                          fv_vi_symuncert$data,
                          fv_vi_relief$data,
                          fv_vi_rank$data, 
                          fv_vi_cor$data, 
                          fv_vi_mrmr$data, 
                          fv_vi_cmim$data, 
                          fv_vi_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:89, 10)) %>% 
  tidyr::spread(method, value) %>% 
  mutate_if(is.numeric, list(~na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

corr = cor(fv_all)
#p.mat = cor_pmat(corr)

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = F,
           type = "lower",
           lab = TRUE)
```

@@

fv_all = dplyr::bind_rows(fv_nri_car$data, 
                          fv_nri_info.gain$data, 
                          fv_nri_gain.ratio$data,
                          fv_nri_symuncert$data,
                          fv_nri_relief$data,
                          fv_nri_rank$data, 
                          fv_nri_cor$data, 
                          fv_nri_mrmr$data, 
                          fv_nri_cmim$data, 
                          fv_nri_var$data) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:7381, 10)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

corr = cor(fv_all)
p.mat = cor_pmat(corr)

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = FALSE,
           type = "lower",
           lab = TRUE)
```

@@

fv_all = dplyr::bind_rows(fv_hr_car$data, 
                          fv_hr_info.gain$data, 
                          fv_hr_gain.ratio$data,
                          fv_hr_symuncert$data,
                          fv_hr_relief$data,
                          fv_hr_rank$data, 
                          fv_hr_cor$data, 
                          fv_hr_mrmr$data, 
                          fv_hr_cmim$data,
                          fv_hr_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id=rep(1:122, 10)) %>% 
  tidyr::spread(method, value) %>% 
  dplyr::select(-id)

corr = cor(fv_all)
p.mat = cor_pmat(corr)

ggcorrplot(corr,
           #p.mat = p.mat,
           hc.order = F,
           type = "lower",
           lab = TRUE)
```

>>>>

# load drake objects
loadd(
  vi_data, nri_data, bands_data, coords_vi_nri_clean,

@@

```{r eda-1 }
intro <- introduce(vi_data)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
knitr::kable(intro_df)
```

@@

```{r eda-5 }
intro <- introduce(nri_data)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-8 }
intro <- introduce(bands_data)
intro_df <- data.frame(
  "Name" = c(
    "Rows", "Columns",
    "Discrete columns", "Continuous columns", "All missing columns",
    "Missing observations", "Complete Rows",
    "Total observations"
  ),
  "Value" = c(
    format(intro[["rows"]], big.mark = ","),
    format(intro[["columns"]], big.mark = ","),
    format(intro[["discrete_columns"]], big.mark = ","),
    format(intro[["continuous_columns"]], big.mark = ","),
    format(intro[["all_missing_columns"]], big.mark = ","),
    format(intro[["total_missing_values"]], big.mark = ","),
    format(intro[["complete_rows"]], big.mark = ","),
    format(intro[["total_observations"]], big.mark = ",")
  )
)
kable(intro_df)
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(479, 451, 300, 529)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```

@@

fv_all <- dplyr::bind_rows(
  fv_vi_car$data,
  fv_vi_info.gain$data,
  fv_vi_gain.ratio$data,
  fv_vi_symuncert$data,
  fv_vi_relief$data,
  fv_vi_rank$data,
  fv_vi_cor$data,
  fv_vi_mrmr$data,
  fv_vi_cmim$data,
  fv_vi_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:89, 10)) %>%
  tidyr::spread(method, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
# p.mat = cor_pmat(corr)

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

@@

fv_all <- dplyr::bind_rows(
  fv_nri_car$data,
  fv_nri_info.gain$data,
  fv_nri_gain.ratio$data,
  fv_nri_symuncert$data,
  fv_nri_relief$data,
  fv_nri_rank$data,
  fv_nri_cor$data,
  fv_nri_mrmr$data,
  fv_nri_cmim$data,
  fv_nri_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:7381, 10)) %>%
  tidyr::spread(method, value) %>%
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
p.mat <- cor_pmat(corr)

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = FALSE,
  type = "lower",
  lab = TRUE
)
```

@@

fv_all <- dplyr::bind_rows(
  fv_hr_car$data,
  fv_hr_info.gain$data,
  fv_hr_gain.ratio$data,
  fv_hr_symuncert$data,
  fv_hr_relief$data,
  fv_hr_rank$data,
  fv_hr_cor$data,
  fv_hr_mrmr$data,
  fv_hr_cmim$data,
  fv_hr_var$data
) %>%
  dplyr::select(value, method) %>%
  mutate(id = rep(1:122, 10)) %>%
  tidyr::spread(method, value) %>%
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
p.mat <- cor_pmat(corr)

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```
